Combine Files

### 2023-05-25 manuscript_scopus.Rmd
updating with a couple things

```{r}
total_num <- 13581
health_num <- 10685
physical_num <- 6151
social_num <- 543
life_num <- 7686
```

@@

```{r}
journals <- 2534
health_journal <- 1472
physical_journal <- 641
social_journal <- 206
life_journal <- 1024
```

@@

```{r tab-snip, results = 'asis', include = TRUE}
apa_table(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)), 
  caption = "Big-Team Science SNIP Values")
```

```{r results = 'asis', include = TRUE}
apa_table(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)),
  caption = "All Journal Articles SNIP Values")
```

@@

```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RUN THIS ###
#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
pub_total <- DF$pub_time_subject %>% 
  group_by(SubjectArea, ASJC) %>% 
  summarize(Count_Size = sum(count), .groups = "keep") %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))

@@

```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RERUN THIS ###
health_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Health Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

```{r}
total_authors <- 257536
avg_authors <- apa_num(49.904646)
sd_authors <- apa_num(207.006114)
min_authors <- 10
med_authors <- 19
max_authors <- 5155
```

@@

```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.531373, -0.437422, -0.460876, -0.604957)
avg_se_values <- c(0.030990, 0.058153, 0.009794, 0.026519)
sd_b_values <- c(-0.207000, -0.104549, -0.218675, -0.056843)
sd_se_values <- c(0.059698, 0.058153, 0.009794, 0.046915)
r2_values <- c(0.145118, 0.118772, 0.144584, 0.175747)
sample_size <- 13000

@@

```{r}
affs <- 35114
```

@@

***Education***.

We will summarize the general education categories of individuals at the
time of publication, along with a summary for change over time.

- For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are "normal" academics/researchers)
- We will only perform this analysis if the proportion of information avaliable is over 50%.

+--------+--------+
| d      | count  |
| egrees |        |
+--------+--------+
| ``` CE | 656440 |
| F7FA46 | 8190   |
|        | 3879   |
|   null | 1267   |
|        | 1002   |
|     MD | 490    |
|        | 461    |
|    PhD | 368    |
| M      | 349    |
| D, PhD | 348    |
|        | 330    |
|   M.D. | 285    |
|        | 279    |
|    Dr. | 266    |
|        | 239    |
|    MSc | 232    |
|        | 220    |
|    MPH | 196    |
| ```    | 191    |
|        | 158    |
| Prof., |        |
| PhD    |        |
| Ph.D.  |        |
| MS MD  |        |
| PhD    |        |
| MD.    |        |
| Prof.  |        |
| MD     |        |
| Prof.  |        |
| PhD BS |        |
| Prof   |        |
| BA     |        |
| M.D.,  |        |
| Ph.D.  |        |
| MD,    |        |
| MPH    |        |
+--------+--------+

@@

```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.004420, -0.335536, -0.235551, -0.430599)
avg_se_values <- c(0.022715, 0.179536, 0.028158, 0.037807)
sd_b_values <- c(-0.105746, 0.130796, -0.006692, 0.133215)
sd_se_values <- c(0.034058, 0.186924, 0.026612, 0.034255)
r2_values <- c(0.009554, 0.021558, 0.035782, 0.054081)
sample_size <- 13000

@@

```{r geo-map}
# serbia has changed codes
DF$geo_country$affiliation_tag_country <- toupper(DF$geo_country$affiliation_tag_country)
DF$geo_country <- subset(DF$geo_country, affiliation_tag_country != "NONE")
DF$geo_country$affiliation_tag_country[DF$geo_country$affiliation_tag_country == "SCG"] <- "SRB"

@@

```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
label <- c("Physical", "Social", "Health", "Life")
b_values <- c(-0.061001, -0.077040, -0.017775, -0.014946)
se_values <- c(0.022958, 0.058153, 0.009794, 0.010485)
r2_values <- c(0.002357, 0.004491, 0.000434, 0.000434)
sample_size <- 13000

>>>>

```{r total-articles}
# updated 
total_num <- 462970
health_num <- 403697
physical_num <- 207192
social_num <- 23020
life_num <- 275249
```

@@

```{r total-journals}
# updated
journals <- 14263
health_journal <- 6301
physical_journal <- 5505
social_journal <- 2314
life_journal <- 4030
```

@@

```{r tab-snip, results = 'asis', include = TRUE}
# updated
apa_table(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)), 
  caption = "Big-Team Science SNIP Values")
```

```{r results = 'asis', include = TRUE}
# updated
apa_table(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)),
  caption = "All Journal Articles SNIP Values")
```

@@

```{r make-clouds, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RUN THIS ###
#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
pub_total <- DF$pub_time_subject %>% 
  group_by(SubjectArea, ASJC) %>% 
  summarize(Count_Size = sum(count), .groups = "keep") %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))

@@

```{r make-clouds2, eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RERUN THIS ###
health_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Health Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

@@

```{r total-authors}
total_authors <- 2786877 # only this updated
avg_authors <- apa_num(49.904646)
sd_authors <- apa_num(207.006114)
min_authors <- 10
med_authors <- 19
max_authors <- 5155
```

@@

```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
# updated
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.694505, -0.364097, -0.450156, -0.510173)
avg_se_values <- c(0.002903, 0.006058, 0.001443, 0.001924)
sd_b_values <- c(-0.284249, -0.134722, -0.136871, -0.052559)
sd_se_values <- c(0.007381, 0.014757, 0.003646, 0.004821)
r2_values <- c(0.461106, 0.253958, 0.299746, 0.346628)
sample_size <- total_num

@@

```{r total-aff}
# updated
affs <- 434092
```

@@

@@

```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
# updated 
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(0.005832, -0.026835, -0.020444, -0.007609)
avg_se_values <- c(0.000189, 0.001245, 0.000230, 0.000231)
sd_b_values <- c(-0.023375, 0.015881, 0.008203, -0.003291)
sd_se_values <- c(0.000255, 0.001118, 0.000220, 0.000265)
r2_values <- c(0.137207, 0.033117, 0.046249, 0.030199)
sample_size <- total_num

@@

```{r geo-map}
# serbia has changed codes
# updated but needs work
DF$geo_country$affiliation_tag_country <- toupper(DF$geo_country$affiliation_tag_country)
DF$geo_country <- subset(DF$geo_country, affiliation_tag_country != "NONE")
DF$geo_country$affiliation_tag_country[DF$geo_country$affiliation_tag_country == "SCG"] <- "SRB"

@@

```{r fig-diversity, include = TRUE, fig.cap= "Number of geopolitical regions represented in big-team science publiactions predicting time and the overall model effect size."}
# updated 
label <- c("Physical", "Social", "Health", "Life")
b_values <- c(0.015622, 0.034822, 0.019287, 0.011870)
se_values <- c(0.002748, 0.006295, 0.001209, 0.001552)
r2_values <- c(0.000315, 0.001822, 0.000926, 0.000371)
sample_size <- total_num
